Lawrence Bull, PhD

### 2024-12-16 index.qmd
papers/bio update

Researcher Fellow at [Glasgow University](https://www.gla.ac.uk/schools/mathematicsstatistics/staff/lawrencebull/#biography) in statistical methods for Data-Centric Engineering, specialising in monitoring techniques for telemetry data from systems and infrastructure.

I'm interested in the dependencies that appear in measurements from populations of machines -- [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [trains](https://arxiv.org/abs/2403.17820), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (... [wind turbines](https://arxiv.org/abs/2111.15496)).
By encoding domain expertise into statistical models, complex representations can be built from interpretable units, allowing machines to share information and increasing the value of data.
<!-- At a systems level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts. -->

>>>>

Researcher Fellow [[Stats, UoG]](https://www.gla.ac.uk/schools/mathematicsstatistics/staff/lawrencebull/#biography) in machine learning for physical systems. Particularly tools to encode structure (via domain knowledge) into data-driven models. Statistical methods for telemetry data from machines and infrastructure.

Applications have included [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [trains](https://arxiv.org/abs/2403.17820), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (.. [wind turbines](https://arxiv.org/abs/2111.15496)).
By encoding domain expertise into statistical models, complex representations can be built from interpretable units, allowing machines to share information and increasing the value of data.
